---
title: "Starting as a Data Scientist"
author: Kayla Kippes
format: html
editor: visual
---

## Question Answers

-   Being a data scientist is about having the technical and story-telling skills to answer complex statistical questions. It is not only being able to talk about the results of data but also manipulating it efficient ways.

-   I think data scientists and statisticians both use statistical methods to analyze data in order to solve real-world problems. However, I think statisticians are more focused on the mathematical rigor behind the analysis whereas data scientists are more focused on the machine learning and process improvements to solve the analysis.

-   I would say I am a healthy blend of both areas. As a Marketing Analyst I am always making sure my methodologies have statistical significance and are deployed correctly but at the same time I am constantly updating and improving upon my processes to make the job easier in the future.

## R Section

Initial R Code:

```{r}
 y <- density(iris$Petal.Width)
```

Determining the class, type, and structure of the object y:

```{r}
#class of y
class(y)
#type of the object y
typeof(y)
#structure of y
str(y)
```

Plotting y but hiding the R code from the final document:

```{r}
#| echo: false
plot(y)
```
